%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\usepackage[super]{nth}
\usepackage{etaremune}
\usepackage[bookmarks=false,colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}
 \name{Justin Melnick}
\begin{document}
% \begin{center}
%     \begin{tabular}{r | l}
% %\multicolumn{2}{c}{ \textbf{\sc Justin Melnick}}\\
%  19 West \nth{4} Street, \nth{2} Floor &\texttt{melnickj@nyu.edu}\\
% New York, NY 10012  & \texttt{justinmelnick.github.io}
% \end{tabular}
% \end{center}
19 West \nth{4} Street, \nth{2} Floor \hfill \texttt{melnickj@nyu.edu}\\
New York, NY 10012 \hfill \texttt{\href{https://justinmelnick.github.io}{justinmelnick.github.io}} \\

\begin{rSection}{Academic Appointments}

{\bf University of Texas at Austin} \hfill { 2027-} \\
Assistant Professor, Department of Government

\vspace*{0.075in}

{\bf Princeton University} \hfill { 2026-2027} 
\\Postdoctoral Research Associate, Niehaus Center for Globalization and Governance
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf New York University} \hfill { 2026 \emph{(expected)}} \\
Ph.D., Politics 
%\begin{itemize}
%   \item Dissertation: ``Essays on the International and Domestic Politics of Climate Policy''
%    \item Committee: Alastair Smith (Chair), Tara Slough, Peter Rosendorff, Sanford Gordon
%\end{itemize}
%M.A., Politics (\emph{2021})\\
\vspace*{0.075in}

{\bf University of Pennsylvania} \hfill { 2020} 
\\B.A., \emph{magna cum laude}, International Relations \emph{(with distinction)} and Economics


\end{rSection}

\begin{rSection}{Research}

\textbf{Peer-Reviewed Articles}
\begin{etaremune}
 \item Melnick, Justin, Alastair Smith, and Bruce Bueno de Mesquita. 2026. \href{https://justinmelnick.github.io/papers/plc/paper.pdf}{Political Life Cycles}.  \textit{Journal of Politics} 88(1): 363-376.
           \item Melnick, Justin. 2025. \href{https://justinmelnick.github.io/papers/exit/paper.pdf}{Domestic Inequality, Heterogeneous Redistribution, and the Globalization Backlash}.  \textit{Journal of Theoretical Politics} 37(4): 319-343.
            \item Melnick, Justin and Alastair Smith. 2025. \href{https://justinmelnick.github.io/papers/paris/paper.pdf}{Shaming Paris: A Political Economy of Climate Commitments}. \textit{International Organization} 79(2): 281-305.
\item Melnick, Justin. 2024. \href{https://justinmelnick.github.io/papers/ets/paper.pdf}{Domestic Politics in the European Union’s Emissions Trading System: Evidence from Free Allowance Allocation}. \textit{Journal of Political Institutions and Political Economy} 5(4): 627-657.
    \item Melnick, Justin and Alastair Smith. 2023. \href{https://justinmelnick.github.io/papers/nego/paper.pdf}{International Negotiations in the Shadow of Elections}.  \textit{Journal of Conflict Resolution} 67(7-8): 1452-1481.
\end{etaremune}

\textbf{Working Papers}
\begin{enumerate}
 \item Melnick, Justin. 2025. \href{https://justinmelnick.github.io/papers/complementarities/paper.pdf}{Learning and Free-Riding in International Climate Policymaking}.
                    \item Melnick, Justin. 2025. \href{https://justinmelnick.github.io/papers/inaction/paper.pdf}{Information and Climate (In)action}.
                        \item Melnick, Justin. 2026. \href{https://justinmelnick.github.io/papers/greens/paper.pdf}{Green Party Vote Shares and Public Support for Climate Policy}.
                        \item Melnick, Justin. 2025. \href{https://justinmelnick.github.io/papers/pledge/paper.pdf}{Pledge-and-Review and Domestic Political Survival}.                        
                        \item Kennard, Amanda and Justin Melnick. 2025. \href{https://justinmelnick.github.io/papers/scam/paper.pdf}{Repealing the ``Green New Scam'': Impacts of the 2024 U.S. Presidential Election on Green Stock Prices}. 
                        \item Melnick, Justin and Alastair Smith. 2026. \href{https://justinmelnick.github.io/papers/electricity/paper.pdf}{Staying in Power, Cutting the Power: Leader Tenure and Electricity Distribution}. 

\end{enumerate}

%\textbf{Work in Progress}
%\begin{enumerate}
%\item Melnick, Justin. 2025. Coordination and Agency Problems in International Climate Finance.
%\item Melnick, Justin. 2025. Leaders and Followers in International Climate Politics.
%\item Kennard, Amanda and Justin Melnick. 2025. Shifting Gears: The Transformation of Climate Governance and the Rise of Green Industrial Policy.
%  %  \item Conevska, Aleksandra and Justin Melnick. 2023. Policy Interventions as Experimental Treatments: Applications to Climate Politics.
%   % \item Castillo-Quintana, Martin and Justin Melnick. 2023. A Theory of the Consequences of Private Military Companies.
%\end{enumerate}
\end{rSection}
%\newpage
\begin{rSection}{Other Writing}
\textbf{Case Studies}
\begin{enumerate}
\item Melnick, Justin. 2023. ``The Politics of Formulating and Implementing Climate Policies in the Netherlands.'' EGAP.
\end{enumerate}

\textbf{Commentary}
    \begin{enumerate}
    \item   Jan, Farah and Justin Melnick. 2020. China's Challenge to America's Political and Economic Liberal Order. \textit{The National Interest}.
    \item    Jan, Farah and Justin Melnick. 2019. After Trump's Hong Kong Democracy Act, China is Still Winning. \textit{Foreign Policy}.
\end{enumerate}
\end{rSection}

\begin{rSection}{Awards and Fellowships}
\begin{itemize}
\item Climate Doctoral Fellow, New York University \hfill 2025-2026
\item Travel Grant, APSA Formal Theory Section \hfill 2024
\item George Downs Prize, New York University \hfill 2024
\item EGAP Politics of Climate Policy Case Study Grant \hfill 2023
\item Dean's Conference Travel Fund, New York University \hfill 2023; 2025
\item Empirical Implications of Theoretical Models (EITM) Summer Institute, Princeton University \hfill 2023
\item Bradley Fellowship \hfill 2023
\item MacCracken Award, New York University \hfill 2021 - 2026
\item Norman D. Palmer Thesis Award, University of Pennsylvania \hfill 2020
\item Rose Undergraduate Research Award, University of Pennsylvania \hfill 2020
\item College Alumni Society Prize in IR, University of Pennsylvania \hfill 2020
\item Global Eminence Fellow, Kyung Hee University \hfill 2018
\end{itemize}
\end{rSection}

\begin{rSection}{Presentations}

\textbf{Invited Presentations}

\begin{table}[!htbp]
    \centering
    \begin{tabular}{@{\hspace*{2em}}p{6.9in}p{1in}@}
    NYU CESS (scheduled); Environmental Politics and Governance (scheduled) & 2026\\\\
    Harvard University; Environmental Politics and Governance; University of Texas at Austin; MIT; University of Wisconsin-Madison & 2025\\\\
    EGAP Climate Change Governance Meeting; NYU  CESS;  Washington University in St. Louis; University of Southern California; London School of Economics & 2024\\\\
      Harvard University; University of Pittsburgh; Empirical Implications of Theoretical Models; Princeton Graduate Climate Lab; GSIPE    & 2023 
    \end{tabular}
\end{table}
      %NYU International Relations Workshop; NYU Comparative Politics Workshop;  NYU Graduate Political Economy Workshop
      %\\
        % NYU International Relations Workshop; NYU Graduate Political Economy Workshop & 2022\\
        % NYU International Relations Workshop & 2021
\textbf{Conference Participation}

\hspace*{0.5em} APSA (2023-2025);  MPSA (2020; 2024-2025); PECE (2023-2025); IPES (2023); Climate Pipeline (2024);\\ \hspace*{0.5em}  NEWEPS (2025)

%\textbf{Internal Workshops}
%
%\hspace*{0.5em} NYU International Relations Workshop (2021-2025); NYU Political Economy Workshop (2025); NYU Comparative Politics Workshop (2023); NYU Graduate Political Economy Seminar (2022-2023); Penn Perry World House Seminar (2019)
\end{rSection}

\begin{rSection}{Teaching}
\textbf{Graduate}
\begin{itemize}
\item Quantitative Analysis IV (Ph.D.) for Prof. Tara Slough \hfill Spring 2026
\item Game Theory I (Ph.D.) for Prof. Ga\'etan Nandong \hfill Spring 2024
\item Quantitative Analysis I (Ph.D.) for Prof. Neal Beck \hfill Fall 2021; Fall 2022
\item Quantitative Analysis I (M.A.) for Prof. Pat Egan \hfill Summer 2021; Summer 2022; Summer 2023
\item Strategic Thinking (Game Theory) (M.S.) for Prof. Mike Ting (Columbia) \hfill Fall 2023; Fall 2024
\end{itemize}
\textbf{Undergraduate}
\begin{itemize}
\item Politics of Climate Change  for Prof. Eric Dickson \hfill Spring 2023; Fall 2025
\item International Politics  for Prof. Nicole Simonelli \hfill Fall 2023
\item Senior Honors Thesis Seminar II  for Prof. Chris Dawes \hfill Spring 2025
\item Senior Honors Thesis Seminar I  for Prof. Alastair Smith \hfill Fall 2024
\item Research Methods for Politics  for Prof. Anna Harvey \hfill Spring 2022
\item U.S. Politics and Policy in 2022 and Beyond  for Prof. Pat Egan \hfill January 2022
\end{itemize}
\end{rSection}

%\begin{rSection}{Research Assistance}
%\begin{itemize}
%\item Prof. Tara Slough (NYU) \hfill 2025
%    \item Prof. Alastair Smith (NYU) \hfill 2022; 2023; 2024
%    \item Prof. Bruce Bueno de Mesquita (NYU) \hfill 2023
%   \item  Prof. Amanda Kennard (Stanford) \hfill 2023
%    \item Prof. Ga\'etan Nandong (NYU) \hfill 2023
%    \item Prof. Neal Beck (NYU) \hfill 2021
%   \item  Stern DHL Globalization Initiative (NYU) \hfill 2020-2021
%   \item  Prof. Beth Simmons (Penn) \hfill 2018-2020
%    \end{itemize}
%\end{rSection}
\begin{rSection}{Service}
\begin{itemize}
\item Reviewer:  \textit{American Journal of Political Science};  \textit{Climatic Change}; \textit{Foreign Policy Analysis}; \textit{Journal of Conflict Resolution}

\item Replication Analyst (Proof Verification):  \textit{International Organization} 
\item Convenor: NYU Graduate Political Economy Workshop (Spring 2023); NYU Political Economy of Climate Change Reading Group (Summer 2024)
\end{itemize}
 \end{rSection}

\begin{rSection}{Skills}
\begin{itemize}
\item Languages: Spanish, French, Italian, Mandarin Chinese [all from a very long time ago]
\item Programming: \texttt{R}, Mathematica, \LaTeX
\item Field Research: 60th Session of the UNFCCC Subsidiary Bodies, Bonn Germany (2024) 
\end{itemize}
\end{rSection}



\end{document}
